Data Analysis

### 2022-05-12 04.manuscript.Rmd
updates from last week

@@

  - The slope for year of first publication was *b* = `r format(round(o_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(o_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r o_career_output$df[2]`) = `r format(round(o_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(o_career_output$p.value[2])`. 
  - The variance parameter was $SD$ = `r format(round(o_career_output$estimate[3], digits = 2), nsmall = 2)`. 
  - The slope for variance across years was *b* = `r format(round(var_o_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_o_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_o_career_model$df.residual`) = `r format(round(var_o_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_o_career_output$p.value[2])`.

@@

  - The slope for year of first publication was *b* = `r format(round(s_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(s_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r s_career_output$df[2]`) = `r format(round(s_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(s_career_output$p.value[2])`. 
  - The variance parameter was $SD$ = `r format(round(s_career_output$estimate[3], digits = 2), nsmall = 2)`. 
  - The slope for variance across years was *b* = `r format(round(var_s_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_s_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_s_career_model$df.residual`) = `r format(round(var_s_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_s_career_output$p.value[2])`.

@@

  - The slope for year of first degree was *b* = `r format(round(o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r o_career_ed_output$df[2]`) = `r format(round(o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(o_career_ed_output$p.value[2])`. 
  - The variance parameter was $SD$ = `r format(round(o_career_ed_output$estimate[3], digits = 2), nsmall = 2)`. 
  - The slope for variance across years was *b* = `r format(round(var_o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_o_career_ed_model$df.residual`) = `r format(round(var_o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_o_career_ed_output$p.value[2])`.

>>>>

**_Employment_**. 
- print out overall
- print out over time 
- comment on if all normal academic

**_Education_**. 
- print out overall
- print out over time

**_Types of Publications_**. 
- print out overall
- print out over time 
- open science question

**_Publication Metrics_**. 
- means and SDs for i10 and hindex information, and number of publications 
- same analyses as career length - slope of number of publications and variance of number of publications 
- slope up means people who are publishing more are more represented in the researchers
- slope down means more people with less publications
- answer are we giving opportunities to people who need the bean counting

**_Geopolitical Regions_**. 
- overall map of where people get their education
- overall map of where people are working 
- is this diversifying over time (more countries as years go up)
- then the weird analysis to answer about diversifying authors

@@

  - The slope for year of first publication was *b* = `r format(round(o_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(o_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r o_career_output$df[2]`) = `r format(round(o_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(o_career_output$p.value[2])`. 
  - The variance parameter was *SD* = `r format(round(o_career_output$estimate[3], digits = 2), nsmall = 2)`. 
  - The slope for variance across years was *b* = `r format(round(var_o_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_o_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_o_career_model$df.residual`) = `r format(round(var_o_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_o_career_output$p.value[2])`.

@@

  - The slope for year of first publication was *b* = `r format(round(s_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(s_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r s_career_output$df[2]`) = `r format(round(s_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(s_career_output$p.value[2])`. 
  - The variance parameter was *SD* = `r format(round(s_career_output$estimate[3], digits = 2), nsmall = 2)`. 
  - The slope for variance across years was *b* = `r format(round(var_s_career_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_s_career_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_s_career_model$df.residual`) = `r format(round(var_s_career_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_s_career_output$p.value[2])`.

@@

  - The slope for year of first degree was *b* = `r format(round(o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r o_career_ed_output$df[2]`) = `r format(round(o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(o_career_ed_output$p.value[2])`. 
  - The variance parameter was *SD* = `r format(round(o_career_ed_output$estimate[3], digits = 2), nsmall = 2)`. 
  - The slope for variance across years was *b* = `r format(round(var_o_career_ed_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_o_career_ed_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_o_career_ed_model$df.residual`) = `r format(round(var_o_career_ed_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_o_career_ed_output$p.value[2])`.
